Concurrent Programming with Harmony

### 2020-07-30 book/paper.tex
Added some info

On the left is a Hoare monitor.
When some process $p$ is in the bathroom, it can invoke \textbf{signal}
on some non-empty bedroom associated with a condition that holds.
This select a process $q$ in that bedroom.
As a result of invoking \textbf{signal}, $p$ goes back into the hall
and $q$ enters the bathroom.
Importantly, when $q$ enters the bathroom, the condition that $q$ was
waiting for is guaranteed to hold.

>>>>

On the left is a Hoare monitor.
When some process $p$ is in the bathroom, it can invoke \textbf{signal}
on some non-empty bedroom associated with a condition that holds.
This select a process $q$ in that bedroom.
As a result of invoking \textbf{signal}, $p$ goes back into the hall
and $q$ enters the bathroom.\footnote{Per Brinch Hansen' monitors have
a \textbf{continue} operation instead of \textbf{signal}.  The difference
is that processes that invoke \textbf{continue} leave the monitor rather
than returning to the hall.}
Importantly, when $q$ enters the bathroom, the condition that $q$ was
waiting for is guaranteed to hold.
